6.830 Project Proposal \\ \large Data Imputation as a Query Optimization

### 2016-10-12 main.tex
proposal: minor typos

\section{Approach}
In order to study the placement of an imputation step, we propose to create a logical imputation operator (along with respective physical instances) and incorporate its placement as part of the query plan optimization process in SimpleDB.  We plan to introduce measures for uncertainty and completeness of query results as well as the cost of imputation, which outline the main tradeoffs in the imputation placement. We introduce these measures into our cost estimation, allowing us to intelligently place the data imputation step during query planning. Finally, we plan to produce empirical results that show the tradeoffs between efficiency and accuracy in the context of simple data imputation models in queries that perform aggregate operations or return a significant number of tuples (in contrast to simple point-queries) and compare to existing approaches.  These types of queries are more likely to provide reasonable cases for imputation of missing values and reflecting an increasingly large portion of workloads in modern OLAP warehouses.

@@

This example shows that the imputation operator, even in its simplest form, can have a significant impact on the query results. Furthermore, this example fails to capture other important dimensions such as cost of imputation.

>>>>

\section{Approach}
In order to study the placement of an imputation step, we propose to create a logical imputation operator (along with respective physical instances) and incorporate its placement as part of the query plan optimization process in SimpleDB.  We plan to introduce measures for uncertainty and completeness of query results as well as the cost of imputation, which outline the main tradeoffs in the imputation placement. We introduce these measures into our cost estimation, allowing us to intelligently place the data imputation step during query planning. Finally, we plan to produce empirical results that show the tradeoffs between efficiency and accuracy in the context of simple data imputation models in queries that perform aggregate operations or return a significant number of tuples (in contrast to simple point-queries) and compare to existing approaches.  These types of queries are more likely to provide reasonable cases for imputation of missing values and reflect an increasingly large portion of workloads in modern OLAP warehouses.

@@

This example shows that the imputation operator, even in its simplest form, can have a significant impact on query results. Furthermore, this example fails to capture other important dimensions such as cost of imputation.
